Draft information

### 2019-08-29 paper/draft-info.Rmd
Update draft info

* Should I include more networks? Easy to get some more from other published studies. Could improve the manuscript but every new data set has to be cleaned independently and might take one to half a day per network.
* Should I increase the resolution of the bioclimatic variables? Currently working with 2.5' (~5km). Increasing to 30'' (~1km) might improve the analysis but we're talking about working with ~25GB+ of data instead of the 1GB used now. 
* Audrey: Could you please fill in the gaps in the rationale behind filtering out occurrences with potential low quality coordinates (\lr{rationale-occurrence-filtering})

@@

* Downloaded network data from the Web of Life and cleaned it. I didn't anticipated data needed SO MUCH work! I estimated three days to do this but took roughly 3 weeks to do it propperly and there is still some work to do. Quite a mess...
* Downloaded bioclimatic and habitat data
* Dowloaded species occurrences. Wasn't straightforward as there is a lot of species and lots of restrictions with the GBIF API. About a week getting this to work.

@@

* Manually fix the remaining species names that are incorrect and were not picked up by the automatic procedure. Doing 5-10 per day, so should be done in a couple months
* Fix references. There are lots of mistakes re. author, years and publication venue.

>>>>

* Should I include more networks? Easy to get some more from other published studies. Could improve the manuscript but every new data set has to be cleaned independently. This could take around 2 days per network.
* Should I increase the resolution of the bioclimatic variables? Currently working with 2.5' (~5km). Increasing to 30'' (~1km) might improve the analysis but we're talking about working with ~25GB+ of data instead of the 1GB used now. 
* Audrey: Could you please fill in the gaps in the rationale behind filtering out occurrences with potential low quality coordinates (\lr{rationale-occurrence-filtering})
* I chose, rather arbitrarily, a mean absolute error of 10% for the sensitivity analysis. Does this choice sound appropiate to you?

@@

* Downloaded network data from the Web of Life and cleaned it. I didn't anticipated data needed SO MUCH work! I estimated three days to do this but took roughly 3 weeks to do it propperly and there is still some work to do. Quite a mess...
* Downloaded bioclimatic and habitat data
* Dowloaded species occurrences. Wasn't straightforward as there is a lot of species and lots of restrictions with the GBIF API. About a week getting this to work.
* Calculated environmental niche size and the environmental suitability of species in their communities
* Modelled the normalised degree of species as a proxy of eltonian niche size using a bayesian framework

@@

* Manually fix the remaining species names that are incorrect and were not picked up by the automatic procedure. Doing 5-10 per day, so should be done in a couple months
* Fix references. There are lots of mistakes re. author, years and publication venue particularly for those from which data was downloaded.
